---
title: "Cropped trend map"
author: "LD"
date: "2023-05-25"
output: html_document
---

Here is an example of how to produce cropped trend maps, including only the regions with trends for a given species.

##Load packages
```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
library(bbsBayes2)
library(sf)
```

###Create your model

Download the Hepatic Tanager GAMYE model, by clicking "Download" here: https://github.com/L-Daly/bbsbae/blob/25eeb0f974bcdf832b8375422a9ac57c046c62c2/data/HETA_bbs_usgs_gamye.rds . OR run the model using the code below, which may take over 20 minutes.
```{r}
mod<-stratify(by="bbs_usgs",species="Hepatic Tanager")%>%
  prepare_data()%>%
  prepare_model(model="gamye",model_variant = "hier")%>%
  run_model(chains=4,iter_warmup = 1000,iter_sampling = 1000)
```

###Prepare your components.
```{r}

```
```{r}
#load a map with the same stratifications
map<-load_map(stratify_by = "bbs_usgs")
#load the trends 
t<-generate_indices(mod)%>%
  generate_trends()
#create dataframe of trends and strata names, removing the continental trend
trend<-data.frame(c(t$trends$trend),c(t$trends$strata_included))[-1,]
names(trend)<-c("Trend","strata_name")
```

###Fine-tune your map
Filter out strata without trends and add the trends to the map.
```{r}
map1<-map%>%
  filter(strata_name %in% strata)
map2<-inner_join(map1,trend,by="strata_name")
```

###Plot it up
Lastly, plot it!
```{r}
ggplot()+
  geom_sf(data=map2,aes(fill=Trend))
```
